Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-09-05 papers/thesis-kirstie/thesis.tex
more cleanup

\begin{equation}{\label{Fidealmultipleint}}{=-k_BT\ln\left(V^N\frac{1}{N!}\frac{1}{h^{3}}\int{d\vec{p}_1}~e^\frac{-\frac{|\vec{p}_1|^2}{2m}}{k_BT}\frac{1}{h^{3}}\int{d\vec{p}_2}~e^\frac{-\frac{|\vec{p}_2|^2}{2m}}{k_BT}{...}\frac{1}{h^{3}}\int{d\vec{p}_N}~e^\frac{-\frac{|\vec{p}_N|^2}{2m}}{k_BT}\right)}\end{equation}
These integrals can conveniently be written in terms of the DeBroglie wavelength $\Lambda$
\begin{equation}{\frac{1}{h^{3}}\int{d\vec{p}}~e^\frac{-\frac{|\vec{p}|^2}{2m}}{k_BT}=\left(\sqrt{\frac{k_BTm}{2\pi\hbar^2}}\right)^3=\frac{1}{\Lambda^{3}}}\end{equation} 
where \begin{equation}{\Lambda =\sqrt{\frac{2\pi\hbar^2}{k_BTm}}}\end{equation} 
Rewriting Equation~\ref{Fidealmultipleint} in terms of $\Lambda$ gives
\begin{equation}{F_{ideal}= -k_BT[\ln(V^N)-\ln(N!) - \ln(\Lambda^{3N})]}\end{equation}Using Stirling's approximation \begin{displaymath}{\ln(N!)=N\ln{N}-N}\end{displaymath} this becomes
\begin{equation}{F_{ideal}= k_BT[N\ln(\frac{N\Lambda^{3}}{V}{)-N}]}\end{equation} 
Rewriting the equation in terms of the number density $n=\frac{N}{V}$, and the quantum volume, $n_Q=\frac{1}{\lambda^3}$ gives
\begin{equation}{F_{ideal}= k_BT\left[\frac{N}{V}\ln{\left(\frac{N}{V}\frac{1}{n_Q}\right)}-\frac{N}{V}\right]}V\end{equation}
\begin{equation}{F_{ideal}= k_BT[n\ln(n/n_Q)-n]V}\label{eq:Fideal}\end{equation}   
For a spatially varying number density, the ideal free energy in Equation~\ref{eq:Fideal} becomes
\begin{equation}{F_{ideal}[n(\vec{r})]= k_BT\int_{Vol}[n(\vec{r})\ln(n(\vec{r})/n_Q)-n(\vec{r})]d\vec{r}}\end{equation}

>>>>

\begin{equation}{\label{Fidealmultipleint}}{=-k_BT\ln\left(V^N\frac{1}{N!}\frac{1}{h^{3}}\int{d\vec{p}_1}~e^\frac{-\frac{|\vec{p}_1|^2}{2m}}{k_BT}\frac{1}{h^{3}}\int{d\vec{p}_2}~e^\frac{-\frac{|\vec{p}_2|^2}{2m}}{k_BT}{...}\frac{1}{h^{3}}\int{d\vec{p}_N}~e^\frac{-\frac{|\vec{p}_N|^2}{2m}}{k_BT}\right)}\end{equation}
These integrals can conveniently be written in terms of the DeBroglie wavelength $\Lambda$, or the quantum volume $\text{n}_\text{Q}$
\begin{equation}{\frac{1}{h^{3}}\int{d\vec{p}}~e^\frac{-\frac{|\vec{p}|^2}{2m}}{k_BT}=\left(\sqrt{\frac{k_BTm}{2\pi\hbar^2}}\right)^3=\frac{1}{\Lambda^{3}}}=\text{n}_\text{Q}\end{equation} 
where \begin{equation}{\Lambda =\sqrt{\frac{2\pi\hbar^2}{k_BTm}}}\end{equation} 
Rewriting Equation~\ref{Fidealmultipleint} in terms of $\Lambda$ gives
\begin{equation}{F_{ideal}= -k_BT[\ln(V^N)-\ln(N!) - \ln(\Lambda^{3N})]}\end{equation}Using Stirling's approximation \begin{displaymath}{\ln(N!)=N\ln{N}-N}\end{displaymath} this becomes
\begin{equation}{F_{ideal}= k_BT[N\ln(\frac{N\Lambda^{3}}{V}{)-N}]}\end{equation} 
Rewriting the equation in terms of the number density $n=\frac{N}{V}$, and the quantum volume, $\text{n}_\text{Q}$ gives
\begin{equation}{F_{ideal}= k_BT\left[\frac{N}{V}\ln{\left(\frac{N}{V}\frac{1}{\text{n}_\text{Q}}\right)}-\frac{N}{V}\right]}V\end{equation}
\begin{equation}{F_{ideal}= k_BT[n\ln(n/\text{n}_\text{Q})-n]V}\label{eq:Fideal}\end{equation}   
For a spatially varying number density, the ideal free energy in Equation~\ref{eq:Fideal} becomes
\begin{equation}{F_{ideal}[n(\vec{r})]= k_BT\int_{Vol}[n(\vec{r})\ln(n(\vec{r})/\text{n}_\text{Q})-n(\vec{r})]d\vec{r}}\end{equation}
